\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2023-12-09 doc/USER_MANUAL/04_creating_databases.tex
- added USE_OTHER_TIME_FUNCTION in Par_file to implement the Brune and Smooth Brune functions for CMTSOLUTION

When using this option, by default the code can locate the force source
anywhere between mesh points in order to honor its exact location; this
is more precise than using the closest GLL mesh point, but it is also a bit slower.
\item [{\texttt{USE\_RICKER\_TIME\_FUNCTION}}] Turn this flag on to use
a Ricker source-time function, i.e., the second derivative of a Gaussian, instead of the source-time functions
set by default to represent a (tilted) \texttt{FORCESOLUTION} force
point source or a \texttt{CMTSOLUTION} moment-tensor source.
Note that we use the standard definition of a Ricker, for a dominant frequency $f_0$:
$\mathrm{Ricker}(t) = (1 - 2 a t^2) e^{-a t^2}$, with $a = \pi^2 f_0^2$,
whose Fourier transform is thus:
$\frac{1}{2} \frac{\sqrt{\pi}\omega^2}{a^{3/2}}e^{-\frac{\omega^2}{4 a}}$
This gives the wavelet of Figure~\ref{fig:RickerWavelet}.
%%
\begin{figure}[htbp]
\centering
\includegraphics[width=3in]{figures/Ricker_wavelet.png}
\caption{We use the standard definition of a Ricker (i.e., second derivative of a Gaussian). Image taken from \url{http://subsurfwiki.org}.}
\label{fig:RickerWavelet}
\end{figure}
%%
Originally, if a \texttt{CMTSOLUTION} moment-tensor source is used, a (pseudo)
Heaviside step function with a very short half duration is defined
for elastic cases to represent the permanent slip on the fault while
in the acoustic case a Gaussian source-time function with a similarly
short half duration is defined to physically describe actions within
the fluid. Otherwise, if a \texttt{FORCESOLUTION} force source is
used, a (pseudo) Dirac delta source-time function is defined by default.
Any other source-time function may then be obtained by convolution.
\item [{\texttt{PRINT\_SOURCE\_TIME\_FUNCTION}}] Turn this flag on to print
information about the source-time function in the file \texttt{OUTPUT\_FILES/plot\_source\_time\_function.txt}.
This feature is only relevant for the solver.
%
\end{description}

>>>>

When using this option, by default the code can locate the force source
anywhere between mesh points in order to honor its exact location; this
is more precise than using the closest GLL mesh point, but it is also a bit slower.
\item [{\texttt{USE\_RICKER\_TIME\_FUNCTION}}] Turn this flag on to use
a Ricker source-time function, i.e., the second derivative of a Gaussian, instead of the source-time functions
set by default to represent a (tilted) \texttt{FORCESOLUTION} force
point source or a \texttt{CMTSOLUTION} moment-tensor source.
Note that we use the standard definition of a Ricker, for a dominant frequency $f_0$:
$\mathrm{Ricker}(t) = (1 - 2 a t^2) e^{-a t^2}$, with $a = \pi^2 f_0^2$,
whose Fourier transform is thus:
$\frac{1}{2} \frac{\sqrt{\pi}\omega^2}{a^{3/2}}e^{-\frac{\omega^2}{4 a}}$
This gives the wavelet of Figure~\ref{fig:RickerWavelet}.
%%
\begin{figure}[htbp]
\centering
\includegraphics[width=3in]{figures/Ricker_wavelet.png}
\caption{We use the standard definition of a Ricker (i.e., second derivative of a Gaussian). Image taken from \url{http://subsurfwiki.org}.}
\label{fig:RickerWavelet}
\end{figure}
%%
Originally, if a \texttt{CMTSOLUTION} moment-tensor source is used, a (pseudo)
Heaviside step function with a very short half duration is defined
for elastic cases to represent the permanent slip on the fault while
in the acoustic case a Gaussian source-time function with a similarly
short half duration is defined to physically describe actions within
the fluid. Otherwise, if a \texttt{FORCESOLUTION} force source is
used, a (pseudo) Dirac delta source-time function is defined by default.
Any other source-time function may then be obtained by convolution.
\item [{\texttt{USE\_OTHER\_TIME\_FUNCTION}}] Turn this flag on to use other source time functions for the CMTSOLUTION (Brune and Smooth Brune). If this flag is on, one line with the other source time function name (\textt{brune} or \texttt{smooth\_brune}) must be added at the end of each \texttt{CMTSOLUTION}.
\item [{\texttt{PRINT\_SOURCE\_TIME\_FUNCTION}}] Turn this flag on to print
information about the source-time function in the file \texttt{OUTPUT\_FILES/plot\_source\_time\_function.txt}.
This feature is only relevant for the solver.
%
\end{description}
